Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-19 prop_iop.tex
prop_iop.tex \section{Examples for Quantum Interval-valued Probability Measures} Updating...

Conversely, given a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfying the above properties, consider $\bar{\mu}:\events\rightarrow\mathscr{I}$
defined by 
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$ and $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item For any $\ket{\psi}\in\mathbb{C}S^{2}$, we have $\bar{\mu}\left(\proj{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
and $\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{\psi}\right)$. 
\end{itemize}
Since other conditions are trivial, we only need to verify equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
First notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
implies equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
by induction. Second, equation~(\ref{eq:QuantumInterval-valuedProbability-Complement})
implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
Therefore, to prove equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
it is sufficient to check 
\begin{equation}
\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)
\end{equation}
for orthogonal $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$. This equation
always holds because the properties of $\bar{f}$.\end{proof}
\begin{definition}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\left(\begin{array}{c}\alpha_{0}\\
\alpha_{1}\\
\alpha_{2}
\end{array}\right)$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\left(\begin{array}{c}\beta_{0}\\
\beta_{1}\\
\beta_{2}
\end{array}\right)$, their cross product is defined as follow: 
\begin{equation}
\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\left|\begin{array}{cc}\alpha_{1}^{*} & \beta_{1}^{*}\\
\alpha_{2}^{*} & \beta_{2}^{*}
\end{array}\right|\ket{0}+\left|\begin{array}{cc}\alpha_{2}^{*} & \beta_{2}^{*}\\
\alpha_{0}^{*} & \beta_{0}^{*}
\end{array}\right|\ket{1}+\left|\begin{array}{cc}\alpha_{0}^{*} & \beta_{0}^{*}\\
\alpha_{1}^{*} & \beta_{1}^{*}
\end{array}\right|\ket{2}\textrm{ ,}
\end{equation}
where $\left|\begin{array}{cc}\alpha & \beta\\
\alpha' & \beta'
\end{array}\right|=\alpha\beta'-\alpha'\beta$. Also, even if $\ket{\psi}$ and $\ket{\phi}$ are normalized, their
cross product~$\ket{\psi}\times\ket{\phi}$ need not be normalized
as usual. We will use $\ket{\psi}\times\ket{\phi}$ and
$\ket{\psi}\times\ket{\phi}/\left\Vert
\ket{\psi}\times\ket{\phi}\right\Vert$ interchanged when there is no
confusion.\end{definition}

@@

Let\emph{ }$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\minus}=\left(\ket{0}-\ket{1}\right)/\sqrt{2}$,
and $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess,\midd\right\} $,

@@

\item The red and green circles are are the states orthogonal to $\ket{0}$

@@

\left[1,1\right]-\bar{f}\left(\ket{\psi_2}\right)\subseteq\bar{f}\left(\ket{\psi_0}\right)+\bar{f}\left(\ket{\psi_1}\right)\textrm{ ,}

@@

for every orthonormal basis~$\mathcal{B}=\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $

@@

equation~(\ref{eq:non-additive-vectors}), and case 1 and 2 are illustrated
in figure~\ref{fig:three-dimensional-5-value}.

@@

\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\midd\subseteq\midd+\imposs=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{0}\right)\textrm{ ,}

@@

\item When $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$, $\ip{\psi_{0}}{0}=0$,
and $\ip{\psi_{1}}{\ps}=0$, we have $\ip{\psi_{2}}{0}\ne0$ and $\ip{\psi_{2}}{\ps}\ne0$.
Then, we have 

@@

\item When $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$, $\ip{\psi_{0}}{0}=0$,
$\ip{\psi_{1}}{0}\ne0$, $\ip{\psi_{1}}{\ps}\ne0$, $\ip{\psi_{2}}{0}\ne0$
and $\ip{\psi_{2}}{\ps}\ne0$. Then, we have 

@@

\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\likely\nsubseteq\unlikely+\midd=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{\psi_0}\right)\textrm{ .}

@@

\footnote{\yutsung{{My previous footnote was wrong. }Need to recompute. Sigh...}}
\item The ``otherwise'' case. Then, equation~(\ref{eq:non-additive-vectors})

@@

$\bar{\mu}$ is convex by theorem~\ref{thm:convex-3}. The following
argument establishes that is has an empty core. Assume there is a
real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
for all $P\in\events$. Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
This measure however is ``better'' than the previous one in the
sense that it might only be induced by $\ket{2}$ or the density matrix
$\mathbb{1}/3$, but not by $\ket{1}$. \end{example}

>>>>

Conversely, given a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfying the above properties, consider $\bar{\mu}:\events\rightarrow\mathscr{I}$
defined by 
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$ and $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item For any $\ket{\psi}\in\mathbb{C}S^{2}$, we have $\bar{\mu}\left(\proj{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
and $\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{\psi}\right)$. 
\end{itemize}
Since other conditions are trivial, we only need to verify equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
First notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
implies equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
by induction. Second, equation~(\ref{eq:QuantumInterval-valuedProbability-Complement})
implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
Therefore, to prove equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
it is sufficient to check 
\begin{equation}
\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)
\end{equation}
for orthogonal $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$,which always
holds because the properties of $\bar{f}$.\end{proof}
\begin{definition}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\left(\begin{array}{c}\alpha_{0}\\
\alpha_{1}\\
\alpha_{2}
\end{array}\right)$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\left(\begin{array}{c}\beta_{0}\\
\beta_{1}\\
\beta_{2}
\end{array}\right)$, their cross product is defined as follow: 
\begin{equation}
\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\left|\begin{array}{cc}\alpha_{1}^{*} & \beta_{1}^{*}\\
\alpha_{2}^{*} & \beta_{2}^{*}
\end{array}\right|\ket{0}+\left|\begin{array}{cc}\alpha_{2}^{*} & \beta_{2}^{*}\\
\alpha_{0}^{*} & \beta_{0}^{*}
\end{array}\right|\ket{1}+\left|\begin{array}{cc}\alpha_{0}^{*} & \beta_{0}^{*}\\
\alpha_{1}^{*} & \beta_{1}^{*}
\end{array}\right|\ket{2}\textrm{ ,}
\end{equation}
where $\left|\begin{array}{cc}\alpha & \beta\\
\alpha' & \beta'
\end{array}\right|=\alpha\beta'-\alpha'\beta$. Also, even if $\ket{\psi}$ and $\ket{\phi}$ are normalized, their
cross product~$\ket{\psi}\times\ket{\phi}$ need not be normalized
as usual. We will use $\ket{\psi}\times\ket{\phi}$ and
$\ket{\psi}\times\ket{\phi}/\left\Vert
\ket{\psi}\times\ket{\phi}\right\Vert$ interchanged when there is no
confusion.\end{definition}

@@

Let\emph{ }$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, and
$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess,\midd\right\} $,

@@

\item The red and green circles are the states orthogonal to $\ket{0}$

@@

\left[1,1\right]-\bar{f}\left(\ket{\psi_2}\right)\subseteq\bar{f}\left(\ket{\psi_0}\right)+\bar{f}\left(\ket{\psi_1}\right)

@@

for every orthonormal basis~$\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $,

@@

equation~(\ref{eq:non-additive-vectors}). Also, to simplify the
notation, we denote $\set{\ket{\psi}}{\ip{\psi}{0}\ne0\textrm{ and }\ip{\psi}{\ps}\ne0}$
by $\mathcal{T}$.

@@

\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\midd=\midd+\imposs=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{0}\right)\textrm{ ,}

@@

\item When $\ip{\psi_{0}}{0}=\ip{\psi_{1}}{\ps}=0$ and $\ket{\psi_{2}}\in\mathcal{T}$,

@@

\item When $\ip{\psi_{0}}{0}=0$, and $\ket{\psi_{1}}$, $\ket{\psi_{2}}\in\mathcal{T}$,

@@

\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\likely\subseteq\unlikely+\midd=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{\psi_0}\right)\textrm{ .}

@@

Similarly, when $\ip{\psi_{0}}{\ps}=0$, $\ket{\psi_{1}}\in\mathcal{T}$,
and $\ket{\psi_{2}}\in\mathcal{T}$, equation~(\ref{eq:non-additive-vectors})
\item When $\ket{\psi_{0}}$, $\ket{\psi_{1}}$, and $\ket{\psi_{2}}\in\mathcal{T}$,
i.e., the ``otherwise'' case. Then, equation~(\ref{eq:non-additive-vectors})

@@

Since we proved that $\bar{\mu}$ is a quantum interval-valued probability
measure, $\bar{\mu}$ is convex by theorem~\ref{thm:convex-3}.

The following argument establishes that $\bar{\mu}$ has an empty
core. Assume there is a real-valued probability measure satisfying
$\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$ for all $P\in\events$. Because
$\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$ and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
\begin{equation}
\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
\end{equation}
\end{example}
